Response to the reviewers’ comments on the article

### 2020-03-29 article_springer/changes.Rmd

---
title: "Response to the reviewers’ comments on the article"  
subtitle: Statistical Inference for inter-arrival times of extreme events in bursty time series 
author: 
  - Katharina Hees
  - Peter Straka
  - Smarak Nayak
date: "11 März 2020"
output: pdf_document
---

@@

* We have also added the following reference: 
Meerschaert, Mark M, and Hans-Peter Scheffler. 2004. “Limit Theorems forContinuous-Time Random Walks with Infinite Mean Waiting Times.”J. Appl.Probab.41 (3): 623–38. https://doi.org/10.1239/jap/1091543414.

@@

* In case of a continuous distribution one can choose the normalization in such a way that a non-degenerate limit distributions exists, but this is not neccessarily true for a linear normalization. We just forgot to add the assumption, that the distribution of the magnitudes is out of the domain of attraction of an extreme value distribution. We added this accordingly.

@@

"(Section 5 and 6) In these 2 sections it is implied that p = k/n .... While a complete rigor in the discussion on the statistical methodology is perhaps not necessary, itis important for the reader to clearly see where “asymptotic approximations” are applied."

* We have re-written Sections 5 & 6, and made sure that $p$ is used as the theoretical exceedance probability, whereas the fraction of exceedances $k/n$ is denoted as $\hat p$. We have also clarified throughout where we assuming approximations.

@@

"(page 11, line 12) Poor scientific language: “... the hill estimator gets useless ... Also a few lines after that, they claim that the scale cannot be estimated. This s not entirely true. The classic work of Peter Hall { entitled On Some Simple Estimates of an Exponent of Regular Variation and published in the Journal of the Royal Statistical Society. Series B (Methodological), Vol. 44, No. 1 (1982), pp. 37(42)does include natural
asymptotically normal estimators for both the tail exponent and the scale. This said, there
is a tremendous amount of work on bias correction for the Hill estimator (and I assume
the scale) that the authors can implement, should they desire. I realize that this may
be going beyond the scope of their work, but proper pointers to the literature should be
given and the notion of second order regular variation (required to establish asymptotic
distributions) should be mentioned."

* KATHI TO DO

"Last but not least, given that the authors are dealing with more or less standard semi- parametric estimation of heavy-tail exponents and scales, they could formulate limit the- orems on the asymptotic distribution of their statistics and derive Wold-type confidence intervals for the estimated parameters. ... "

@@

1.  fixed
2.  fixed
3.  fixed
4.  fixed
5.  fixed
6.  fixed
7.  fixed
8.  fixed
9.  fixed
10. fixed
11. fixed
12. fixed
13. fixed
14. fixed
15. We reformulated the whole part and added titles. 
16. fixed
17. no longer applies
18. fixed
19. fixed
20. fixed
21. fixed
22. fixed
23. fixed
24. fixed
25. fixed
26. The section has been re-written
27. fixed
28. fixed
29. fixed
30. fixed
31. fixed
32. fixed
33. We have commented as follows: 
    "The stability plot for the tail stabilizes nicely around 0.85 (dashed line), while 
    the scale parameter stabilizes less obviously near $3 \times 10^7$ (dashed line).
    The growth of the scale parameter for lower threshold appears to be closer to linear in $p$, 
    rather than proportional to $p^{1/0.85}$ as suggested by the Mittag-Leffler
    fits. The reason for this is likely that the overall goodness of fit as 
    compared to an exponential distribution is improved due to the 
    peaked shape of the Mittag-Leffler distribution near $0$,
    rather than its tail behaviour at $\infty$.
    The reported fit should hence come with the caveat that a Mittag-Leffler 
    distribution models exceedance times well only up to certain time-scales. 
    More research is needed into the modelling of scale transitions, where
    inter-exceedance times appear to have different power laws across different 
    time scales."
34. We have changed "fitted" to "estimated".
35. We have added confidence limits.
36. We have added titles to the two figures, and to other figures where 
    feasible. 
37. fixed
38. fixed

@@

"I understand the authors find inspiration in Peaks-Over-Threshold (POT)
method of extreme value theory, although, I do not see a real connection be-
tween two models. Observe that the peaks over threshold l are ignored, so
random variable $\tau(l)$ could be substituted by any other independent geo-
metric (or exponential) random variable with mean $1/p(l)$."

*

"Moreover, I think, this would simplify some arguments, including the proof of the theorem."

* TO DO

@@

* To DO

@@

* To DO

"The authors finally apply two methods (log-moments and MLE) to es-
timate parameters of the limiting Mittag-Leffler distribution, and obtain in
the process an estimator of the key tail parameter $\beta$. These methods seems
to outperform the standard Hill estimator in a simulation study although
the latter utilizes a much larger data set typically. This phenomena asks
for at least some explanation and a further study, because if it holds more
generally, the authors could use their approach as a superior alternative to
the Hill estimator for any power law distribution with $\beta$ < 1."

* TO DO

@@

* TO DO

"I also do not see a clear connection with the POT method suggested in the abstract, mainly because exceedances really play insignifficant role in the analysis.""

* TO DO

@@

* We added a definition for the left and the right point.
  NOCH ETWAS ZU DEN J_k ERGAENZEN.

@@

* You are completely right again. This was also a typo. We changed this accordingly.

@@

"P.5. You seem to to assume that your $l$ grows at a very precise rate - could this be a problem?"

* PETER TO DO

@@

* We added some more explanation to the last two lines.

@@

* TO DO

@@

* In the pareto case the Hill estimator is less biased, but in all cases it has a higher variance compared to the other two estimators. We reformulated this part.

@@

* This is an approximation. We replaced the equality sign by the approximately-equal sign.

>>>>

---
title: "Response to the reviewers’ comments on the article"  
subtitle: Statistical Inference for inter-arrival times of extreme events in bursty time series 
author: 
  - Katharina Hees
  - Peter Straka
  - Smarak Nayak
date: "11 März 2020"
bibliography: CTRMstats.bib
output: pdf_document
---

@@

* We have also added the following reference: 
Meerschaert, Mark M, and Hans-Peter Scheffler. 2004. “Limit Theorems for Continuous-Time Random Walks with Infinite Mean Waiting Times.”J. Appl.Probab.41 (3): 623–38. https://doi.org/10.1239/jap/1091543414.

@@

* In case of a continuous distribution one can choose the normalization in such a way that a non-degenerate limit distributions exists, but this is not necessarily true for a linear normalization. We just forgot to add the assumption, that the distribution of the magnitudes is out of the domain of attraction of an extreme value distribution. We added this assumption in Section 2.

@@

"(Section 5 and 6) In these 2 sections it is implied that p = k/n .... While a complete rigor in the discussion on the statistical methodology is perhaps not necessary, it is important for the reader to clearly see where “asymptotic approximations” are applied."

* We have re-written Sections 5 & 6, and made sure that $p_l$ is used as the theoretical exceedance probability, whereas the fraction of exceedances $k/n$ is denoted as $\hat p_l$. We have also clarified throughout where we assuming approximations.

@@

"(page 11, line 12) Poor scientific language: “... the hill estimator gets useless ... Also a few lines after that, they claim that the scale cannot be estimated. This is not entirely true. The classic work of Peter Hall ( entitled On Some Simple Estimates of an Exponent of Regular Variation and published in the Journal of the Royal Statistical Society. Series B (Methodological), Vol. 44, No. 1 (1982), pp. 37(42) does include natural asymptotically normal estimators for both the tail exponent and the scale. This said, there
is a tremendous amount of work on bias correction for the Hill estimator (and I assume
the scale) that the authors can implement, should they desire. I realize that this may
be going beyond the scope of their work, but proper pointers to the literature should be
given and the notion of second order regular variation (required to establish asymptotic
distributions) should be mentioned."

* Thank you for this valuable hint and the reference for the article of Peter Hall. We added a sentence regarding bias-reduced versions of the Hill estimator at the end of Section 4. Moreover, we decided to discard the Hill estimator from the simulation study since we already gave at the end of Section 4 sufficient arguments, why we propose to use a parametric estimator based on the Mittag-Leffler distribution instead of a general tail index estimator. Otherwise this would just confuse the reader.

"Last but not least, given that the authors are dealing with more or less standard semi-parametric estimation of heavy-tail exponents and scales, they could formulate limit theorems on the asymptotic distribution of their statistics and derive Wold-type confidence intervals for the estimated parameters. ... "

@@

1.  fixed
2.  fixed
3.  fixed
4.  fixed
5.  fixed
6.  fixed
7.  fixed
8.  fixed
9.  fixed
10. fixed
11. fixed
12. fixed
13. fixed
14. fixed
15. We reformulated the whole part and added titles. 
16. fixed
17. no longer applies
18. fixed
19. fixed
20. fixed
21. fixed
22. fixed
23. fixed
24. fixed
25. fixed
26. The section has been re-written
27. fixed
28. fixed
29. fixed
30. fixed
31. fixed
32. fixed
33. We have commented as follows: 
    "The stability plot for the tail stabilizes nicely around 0.9 (dashed line), while 
    the scale parameter stabilizes less obviously near $3 \times 10^7$ (dashed line).
    The growth of the scale parameter for lower threshold appears to be closer to linear in $p$, 
    rather than proportional to $p^{1/0.9}$ as suggested by the Mittag-Leffler
    fits. The reason for this is likely that the overall goodness of fit as 
    compared to an exponential distribution is improved due to the 
    peaked shape of the Mittag-Leffler distribution near $0$,
    rather than its tail behaviour at $\infty$.
    The reported fit should hence come with the caveat that a Mittag-Leffler 
    distribution models exceedance times well only up to certain time-scales. 
    More research is needed into the modelling of scale transitions, where
    inter-exceedance times appear to have different power laws across different 
    time scales."
34. We have changed "fitted" to "estimated".
35. We have added confidence limits.
36. We have added titles to the two figures, and to other figures where 
    feasible. 
37. fixed
38. fixed

@@

"I understand the authors find inspiration in Peaks-Over-Threshold (POT)
method of extreme value theory, although, I do not see a real connection be-
tween two models. Observe that the peaks over threshold l are ignored, so
random variable $\tau(l)$ could be substituted by any other independent geo-
metric (or exponential) random variable with mean $1/p(l)$. Moreover, I think, this would simplify some arguments, including the proof of the theorem."

* One connection to the Peaks-Over-Threshold (POT) method is, that one has to apply the classical POT approach to the magnitudes. To make this more clear for the reader, we added a comment at the beginning of Section 4. Additionally, inspirited by the POT method, as you said, we propose to fit the inter-exceedance times in a similar fashion: namely, by fitting a Mittag-Leffler distribution to the inter-exceedance times between the peaks over threshold via stability plots. It is true, that the underlying distribution of the magnitudes, in the way we defined the algorithm, gets nearly ignored. A probable extension of our algorithm could be to approximate the tail probability $p_{\ell}$ for very large thresholds by the GPD distribution, which was in a step before fitted to the magnitudes. We add a remark on this after the algorithm.

@@

* The CTRE model is not intended as a substitute for the usual cluster models. It should be more seen as a complement. If there are dependencies in the data, one should first decluster the data. If there are still clusters after (see for example p.3 in @towe2020modelling), the CTRE can maybe account for this behavior. We add a comment on this to the Discussion & Conclusion.

@@

* That is of course true. We calculated here the auto-correlations under the assumption that the underlying data is Mittag-Leffler distributed. The log-Moments of a Mittag-Leffler distribution exist. We added a comment on this in Section 7 to the part "i.i.d.". It is also true that the log-transformation can influence the appearance of the graph. ACFs can always just discover linear dependencies. However, this is just a diagnostic tool to indicate whether the independence assumption is justified. We added for this a comment in the manuscript as well in Section 7 after describing the diagnostic tools.

"The authors finally apply two methods (log-moments and MLE) to estimate parameters of the limiting Mittag-Leffler distribution, and obtain in the process an estimator of the key tail parameter $\beta$. These methods seems to outperform the standard Hill estimator in a simulation study although
the latter utilizes a much larger data set typically. This phenomena asks
for at least some explanation and a further study, because if it holds more
generally, the authors could use their approach as a superior alternative to
the Hill estimator for any power law distribution with $\beta$ < 1."

* It's in interesting idea to use the proposed method for the estimation of the tail index for any power law with $\beta$ < 1. However, this goes beyond the scope of our article. In our article we know from the theory that the inter-exceedance times which we want to model are approximately Mittag-Leffler distributed, hence its natural to use here specific Mittag-Leffler scale and tail estimators.

@@

* We revised the whole manuscript according typos, added the missing assumption for the magnitudes and replaced the proof of the theorem by a new, simplified version (EVTL NOCH ANPASSEN).

"I also do not see a clear connection with the POT method suggested in the abstract, mainly because exceedances really play insignifficant role in the analysis."

* See above.

@@

* We added a definition for the left and the right point. For the role of the magnitudes, see above.

@@

* You are completely right again. This was also a typo. We fixed that.

@@

"P.5. You seem to assume that your $l$ grows at a very precise rate - could this be a problem?"

* TO DO (evtl noch anpassen) We gave a completely new proof. Hence this point no longer applies.

@@

* (EVTL noch anpassen) We added some more explanation to the last two lines.

@@

* For very small tail indices, the (R)MSE is large due to a large variance that results from the fact that in case of a very small tail index single very large events can happen. In the submitted version of the article the simulation study was based on one thousand simulation runs. This was maybe a little bit too small, hence I repeated the study with five thousand runs and now the MSE looks for very small indices more acceptable. I also changed to RMSE since it is easier to interpret.

@@

* In the Pareto case the Hill estimator is less biased, but in all cases it has a higher variance compared to the other two estimators. We reformulated the whole part.

@@

* This is an approximation. We changed "equals" to "is approximately equal to".
